% Bilblio:
\newcommand{\aap}{Astron. \& Astrophys.}
\newcommand{\aasup}{Astron. \& Astrophys. Suppl. Ser.}
\newcommand{\aj}{Astron. J.}
\newcommand{\aph}{Acta Phys.}
\newcommand{\act}{Acta Cryst.}
\newcommand{\actc}{Acta Cryst.}
\newcommand{\acta}{Acta Cryst. A}
\newcommand{\actb}{Acta Cryst. B}
\newcommand{\advp}{Adv. Phys.}
\newcommand{\ajp}{Amer. J. Phys.}
\newcommand{\ajm}{Amer. J. Math.}
\newcommand{\amsci}{Amer. Sci.}
\newcommand{\anofd}{Ann. Fluid Dyn.}
\newcommand{\am}{Ann. Math.}
\newcommand{\ap}{Ann. Phys. (NY)}
\newcommand{\adp}{Ann. Phys. (Leipzig)}
\newcommand{\ao}{Appl. Opt.}
\newcommand{\apl}{Appl. Phys. Lett.}
\newcommand{\app}{Astroparticle Phys.}
\newcommand{\apj}{Astrophys. J.}
\newcommand{\apjsup}{Astrophys. J. Suppl.}
\newcommand{\apss}{Astrophys. Space Sci.}
\newcommand{\araa}{Ann. Rev. Astron. Astrophys.}
\newcommand{\baas}{Bull. Amer. Astron. Soc.}
\newcommand{\baps}{Bull. Amer. Phys. Soc.}
\newcommand{\cmp}{Comm. Math. Phys.}
\newcommand{\cpam}{Commun. Pure Appl. Math.}
\newcommand{\cppcf}{Comm. Plasma Phys. \& Controlled Fusion}
\newcommand{\cpc}{Comp. Phys. Comm.}
\newcommand{\cms}{Comp. Mat. Sci.}
\newcommand{\cqg}{Class. Quant. Grav.}
\newcommand{\cra}{C. R. Acad. Sci. A}
\newcommand{\crv}{Chem. Rev.}
\newcommand{\cp}{Chem. Phys.}
\newcommand{\cma}{Chem. Mater.}
\newcommand{\epl}{Eur. Phys. Lett.}
\newcommand{\ejm}{Eur. J. Mineral.}
\newcommand{\fed}{Fusion Eng. \& Design}
\newcommand{\ft}{Fusion Tech.}
\newcommand{\grg}{Gen. Relativ. Gravit.}
\newcommand{\ieeens}{IEEE Trans. Nucl. Sci.}
\newcommand{\ieeeps}{IEEE Trans. Plasma Sci.}
\newcommand{\ijimw}{Interntl. J. Infrared \& Millimeter Waves}
\newcommand{\ip}{Infrared Phys.}
\newcommand{\irp}{Infrared Phys.}
\newcommand{\jap}{J. Appl. Phys.}
\newcommand{\jac}{J. Appl. Cryst.}
\newcommand{\jacs}{J. Am. Chem. Soc.}
\newcommand{\jamcs}{J. Am. Ceram. Soc.}
\newcommand{\jasa}{J. Acoust. Soc. America}
\newcommand{\jcp}{J. Chem. Phys.}
\newcommand{\jcop}{J. Comp. Phys.}
\newcommand{\jetp}{Sov. Phys.--JETP}
\newcommand{\jetpl}{JETP Lett.}
\newcommand{\jfe}{J. Fusion Energy}
\newcommand{\jfm}{J. Fluid Mech.}
\newcommand{\jmp}{J. Math. Phys.}
\newcommand{\jne}{J. Nucl. Energy}
\newcommand{\jnec}{J. Nucl. Energy, C: Plasma Phys., Accelerators, Thermonucl. Res.}
\newcommand{\jncs}{J. Non-Cryst. Solids.}
\newcommand{\jnm}{J. Nucl. Mat.}
\newcommand{\joam}{J. Optoelect. Adv. Mat.}
\newcommand{\jpcssp}{J. Phys. C: Solid State Phys.}
\newcommand{\jpc}{J. Phys. Chem.}
\newcommand{\jpcs}{J. Phys. Chem. Sol.}
\newcommand{\jpcm}{J. Phys.: Cond. Mat.}
\newcommand{\jpp}{J. Plasma Phys.}
\newcommand{\jpsj}{J. Phys. Soc. Japan}
\newcommand{\jqc}{J. Quant. Chem.}
\newcommand{\jssc}{J. Sol. Stat. Chem.}
\newcommand{\jsi}{J. Sci. Instrum.}
\newcommand{\jvst}{J. Vac. Sci. \& Tech.}
\newcommand{\mcp}{Mat. Chem. Phys.}
\newcommand{\molp}{Mol. Phys.}
\newcommand{\nat}{Nature}
\newcommand{\nature}{Nature}
\newcommand{\nedf}{Nucl. Eng. \& Design/Fusion}
\newcommand{\nf}{Nucl. Fusion}
\newcommand{\nim}{Nucl. Inst. \& Meth.}
\newcommand{\nimpr}{Nucl. Inst. \& Meth. in Phys. Res.}
\newcommand{\np}{Nucl. Phys.}
\newcommand{\npb}{Nucl. Phys. B}
\newcommand{\ntf}{Nucl. Tech./Fusion}
\newcommand{\npbpc}{Nucl. Phys. B (Proc. Suppl.)}
\newcommand{\inc}{Nuovo Cimento}
\newcommand{\nc}{Nuovo Cimento}
\newcommand{\pcg}{Phys. Chem. Glasses}
\newcommand{\pf}{Phys. Fluids}
\newcommand{\pfa}{Phys. Fluids A: Fluid Dyn.}
\newcommand{\pfb}{Phys. Fluids B: Plasma Phys.}
\newcommand{\pl}{Phys. Lett.}
\newcommand{\pla}{Phys. Lett. A}
\newcommand{\plb}{Phys. Lett. B}
\newcommand{\prep}{Phys. Rep.}
\newcommand{\pnas}{Proc. Nat. Acad. Sci. USA}
\newcommand{\pp}{Phys. Plasmas}
\newcommand{\ppcf}{Plasma Phys. \& Controlled Fusion}
\newcommand{\phitrsl}{Philos. Trans. Roy. Soc. London}
\newcommand{\plmb}{Phil. Mag. B} 
\newcommand{\pml}{Phil. Mag. Lett.}
\newcommand{\pmm}{Phil. Mag.}
\newcommand{\prl}{Phys. Rev. Lett.}
\newcommand{\pr}{Phys. Rev.}
\newcommand{\physrev}{Phys. Rev.}
\newcommand{\pra}{Phys. Rev. A}
\newcommand{\prb}{Phys. Rev. B}
\newcommand{\prc}{Phys. Rev. C}
\newcommand{\prd}{Phys. Rev. D}
\newcommand{\pre}{Phys. Rev. E}
\newcommand{\ps}{Phys. Scripta}
\newcommand{\pstb}{Phys. Stat. Sol. b}
\newcommand{\procrsl}{Proc. Roy. Soc. London}
\newcommand{\rmp}{Rev. Mod. Phys.}
\newcommand{\rsi}{Rev. Sci. Inst.}
\newcommand{\rpp}{Rep. Prog. Phys.}
\newcommand{\science}{Science}
\newcommand{\sciam}{Sci. Am.}
\newcommand{\susc}{Surf. Sci}
\newcommand{\sam}{Stud. Appl. Math.}
\newcommand{\sjpp}{Sov. J. Plasma Phys.}
\newcommand{\spd}{Sov. Phys.--Doklady}
\newcommand{\sptp}{Sov. Phys.--Tech. Phys.}
\newcommand{\spu}{Sov. Phys.--Uspeki}
\newcommand{\skt}{Sky and Telesc.}
\newcommand{\ssi}{Solid State Ionics}
\newcommand{\ssc}{Solid State Com.}
\newcommand{\ssnmr}{Solid State Nuc. Mag. Res.}
\newcommand{\zfp}{Zs. f. Phys.}
\newcommand{\zk}{Z. Kristallogr.}

